Observing Economic Growth in Unrecognized States with Nighttime Light \thanks{I thank Elizaveta Kugaevskaia for her superb research assistance on this project. Financial support from Japan Society for the Promotion of Science (JSPS Kakenhi Grant Number 17K13730) is gratefully acknowledged.}

### 2019-03-20 paper/paper.tex
Revise the background section after proof-reading #51

\section{Background}\label{background}
In this section, we provide a brief overview of (1) the international law origin of unrecognized states; (2) causes and consequences of the wars of secession after the collapse of the Soviet Union; (3) state-building efforts, political institutions and economic situations in the four unrecognized states since then.
\subsection{State Recognition in International Law}\label{intl_law}
International law requires a sovereign state to possess (i) a permanent population, (ii) a defined territory, (iii) government, and (iv) capacity to enter into inter-state relations.%
\footnote{
	These four qualifications for a sovereign state were set out in Article I of the Montevideo Convention on Rights and Duties of States, a treaty signed by countries in the American continent in 1933.
	}
However, it is other sovereign states that judge whether a candidate state satisfies these four requirements (Ryngaert and Sobrie 2011472--473).
Consequently, a sovereign state requires recognition by other states.

%On the other hand, a peremptory norm, or \textit{jus cogens}, in international law prohibits the recognition of entities as states if they come into being through the violation of international law such as massive violations of human rights.

%The break-up of Yugoslavia in 1991, starting with Slovenia and Croatia declaring independence, made Western Europe set new standards for recognizing states.%
%\footnote{
%	These new standards are set out in the Declaration on the Guidelines on the Recognition of New States in Eastern Europe and in the Soviet Union on 23 December, 1991.
%} 
%Most significantly, these standards include the commitment to democratic government by the new entities.

@@

\paragraph{Nagorno-Karabakh in Azerbaijan}
Nagorno-Karabakh is a mountainous enclave of Armenian people in the west of Azerbaijan. 
Armenians are culturally different from Azerbaijanis in terms of religion (Armenian Orthodox Christianity versus Islam, mostly Shia) and language (Armenian vs Turkish).

@@

In Nagorno-Karabakh, the war of secession continued from January 1992 to May 1994. The death toll estimate ranges from 17,000 to 25,000 (de Waal 2013:\ 326--327). One significant consequence of the war is ethnic homogenization on both sides of the ceasefire line. 
It is estimated that approximately 500,000 Azerbaijanis were displaced from the occupied part of Azerbaijan while 353,000 Armenians were displaced from the rest of Azerbaijan.%
\footnote{
	These numbers are based on Arif Yunusov's calculations, cited by de Waal (2013:\ 327).
}

In Abkhazia, the war started with the invasion of Georgian troops into Abkhazia in August 1992. 
By the ceasefire in September 1993, however, Abkhaz forces took control of its territory.
The death toll is estimated to be 35,000 (Toal and O'Loughlin 2017:\ 109), and almost all of 239,872 ethnic Georgians in Abkhazia, according to the 1989 census (International Crisis Group 2010:\ fn.75), had been forcefully displaced. 
As the 1989 census records the population of 535,634 in Abkhazia (ACASIAN 2014), the war damage was significant.

@@

In Abkhazia, the opposition candidate won the presidential election in 2004 despite Moscow's support for the incumbent who had been in office since 1994.

In South Ossetia, the first president Lyudvig Chibirov, elected in 1996, was defeated by Eduard Kokoity in the 2001 presidential election (Freedom House 2009).
The parliament rejected an attempt by Kokoity's supporters to lift term limits for presidency in June 2011 (Freedom House 2012).
While the Supreme Court annulled the 2011 presidential election, barring the winning opposition candidate from assuming office, the subsequent election in the following year saw Leonid Tibilov, unrelated to the previous president, sworn in office.%
\footnote{
	In 2017, President Tibilov failed to be re-elected; opposition leader Anatoly Bibilov won the election (Freedom House 2018).
}

@@

South Ossetia had little functioning industry or export-oriented agriculture, with thriving trade activities along the highway linking Georgia to the south with Russia to the north.

>>>>

\section{Background}\label{background}
In this section, we provide a brief overview of (1) the international law origin of unrecognized states; (2) causes and consequences of the wars of secession after the collapse of the Soviet Union; (3) state-building efforts, political institutions and economic situations in the four unrecognized states since then.
\subsection{State Recognition in International Law}\label{intl_law}
International law requires a sovereign state to possess (i) a permanent population, (ii) a defined territory, (iii) government, and (iv) capacity to enter into inter-state relations.%
\footnote{
	These four qualifications for a sovereign state were set out in Article I of the Montevideo Convention on Rights and Duties of States, a treaty signed by countries in the American continent in 1933.
	}
Whether a candidate state satisfies these four requirements, however, is up to the judgement by other sovereign states (Ryngaert and Sobrie 2011:\ 472--473).
Consequently, a sovereign state requires recognition by other states.

@@

\paragraph{Nagorno-Karabakh in Azerbaijan}
Nagorno-Karabakh is a mountainous enclave of Armenian people in the west of Azerbaijan. 
Armenians are culturally different from Azerbaijanis in terms of religion (Armenian Orthodox Christianity versus Islam, mostly Shia) and language (Armenian vs a Turkish language).

@@

In Nagorno-Karabakh, the war of secession continued from January 1992 to May 1994. The death toll estimate ranges from 17,000 to 25,000 (de Waal 2013:\ 326--327). A more significant consequence of the war is ethnic homogenization on both sides of the ceasefire line. 
It is estimated that approximately 500,000 Azerbaijanis were displaced from the occupied part of Azerbaijan while 353,000 Armenians were displaced from the rest of Azerbaijan.%
\footnote{
	These numbers are based on Arif Yunusov's calculations, cited by de Waal (2013:\ 327).
}

In Abkhazia, the war started with the invasion of Georgian troops into Abkhazia in August 1992. 
By the ceasefire in September 1993, however, Abkhaz forces took control of its territory.
The death toll is estimated to be 35,000 (Toal and O'Loughlin 2017:\ 109), and almost all of 239,872 ethnic Georgians in Abkhazia had been forcefully displaced.%
\footnote{
	The population of ethnic Georgians in Abkhazia is based on the 1989 census, cited by International Crisis Group (2010:\ footnote 75).
} 
As the 1989 census records the population of 535,634 in Abkhazia (ACASIAN 2014), the war damage was significant.

@@

In Abkhazia, an opposition candidate, Sergei Bagapsh, became president after winning the 2004 presidential election despite the initial reluctance of Vladislav Ardzinba, the incumbent president who had been in office since 1994, and his designated successor to accept their defeat (Freedom House 2006).

In South Ossetia, the first president Lyudvig Chibirov, elected in 1996, was defeated by Eduard Kokoity in the 2001 presidential election (Freedom House 2009).
In June 2011, the parliament rejected an attempt by Kokoity's supporters to lift term limits for presidency (Freedom House 2012).
While the Supreme Court annulled the 2011 presidential election, barring the winning opposition candidate from assuming office, the subsequent election in the following year saw Leonid Tibilov, unrelated to the previous president, sworn in office.%
\footnote{
	In 2017, President Tibilov failed to be re-elected; opposition leader Anatoly Bibilov won the election (Freedom House 2018).
}

@@

South Ossetia had little functioning industry or export-oriented agriculture. However, trade activities were thriving along the highway linking Georgia to the south with Russia to the north.
